Network Cascades

### 2016-08-25 paper/paper.tex
Add section for summary
Write a summary

@@

>>>>

% TODO: Explanation of the cascade window boundaries/regimes

@@

\section{Summary}\label{sec:summary}

In his paper, Watts introduced a network-theoretical model to explain the occurrance of network cascades. The model is analyzed analytically and empirically and at least for some graph classes conditions for cascades are found. There are two so called regimes of these conditions: One where average degree of the network is low and the threshold is unimportant. Here the cascade size exhibits a power law distribution. As the average degree increases, the threshold under the fraction of neighboring activated nodes must lie must decrease in order to retain vulnerability, and thus becomes the limiting factor. Here the distribution of the cascade size is bimodal, with many small cascades and some very large cascades. Also further effects of network properties are examined.

We motivated this model and explained it in detail. The mathematical details of the analysis have been intentionally left out, but its general approach was shown with more complementary explanations to the derived figures in Watts' paper. Finally, Watts' findings and their interpretation have been reported on.
